---
title: "01 Intro to the tidyverse"
author: "Wahidur Rahman Upal"
date: "07-05-2021"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highes revenue? Replace your bike_orderlines_wrangled_tbl object with the newly wrangled object (with the columns state and city).

```{r}
library(tidyverse)
library(readxl)
library(lubridate)

bikes_tbl      <- read_excel("C:\\Users\\upal1\\Desktop\\DS basic project\\ds_data\\01_bike_sales\\01_raw_data\\bikes.xlsx")
orderlines_tbl <- read_excel("C:\\Users\\upal1\\Desktop\\DS basic project\\ds_data\\01_bike_sales\\01_raw_data\\orderlines.xlsx")
# Not necessary for this analysis, but for the sake of completeness
bikeshops_tbl  <- read_excel("C:\\Users\\upal1\\Desktop\\DS basic project\\ds_data\\01_bike_sales\\01_raw_data\\bikeshops.xlsx")
# 3.0 Examining Data ----
# Method 1: Print it to the console
orderlines_tbl
# Method 2: glimpse
glimpse(orderlines_tbl)
# 4.0 Joining Data ----
left_join(orderlines_tbl, bikes_tbl, by = c("product.id" = "bike.id"))
# Chaining commands with the pipe and assigning it to order_items_joined_tbl
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
# Examine the results with glimpse()
bike_orderlines_joined_tbl %>% glimpse()
# 5.0 Wrangling Data ----
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  
  
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ",") %>%
  
  
  mutate(total.price = price * quantity) %>%
 
  select(-...1, -gender) %>%
 
  select(-ends_with(".id")) %>%
  
 
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  

  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
# 6.1 Sales by Year ----

# Step 1 - Manipulate
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(order_date, total_price) %>%
  
  # Add year column
  mutate(year = year(order_date)) %>%
  
  # Grouping by year and summarizing sales
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
  
  
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
sales_by_year_tbl
# Step 2 - Visualization
sales_by_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales)) +
  
  # Geometries
  geom_col(fill = "springgreen2") + 
  geom_label(aes(label = sales_text)) + 
  geom_smooth(method = "lm", se = FALSE) + 
  

  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )

```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.



Analyze the sales by location and year (facet_wrap). Because there are 12 states with bike stores, you should get 12 plots.
```{r}


# 6.1 Sales by Year state ----
# Step 1 - Manipulate
sales_by_year_cat_1_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  

  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%

  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_year_cat_1_tbl 
# Step 2 - Visualize
sales_by_year_cat_1_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
# Geometries
geom_col() + 
geom_smooth(method = "lm", se = FALSE) +
theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
facet_wrap(~ state) +
scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                  decimal.mark = ",", 
                                                  prefix = "", 
                                                  suffix = " €")) +
labs(
  title = "Revenue by Year and State",
  subtitle = "Drop in sales are fairly low",
  fill = "State" # Changes the legend name
) +
  
  theme_light() +
  theme(title = element_text(face = "bold", color = "brown4"),
        legend.position  = "right",
        axis.text.x = element_text(angle = 45))


```